Baseline centering problem

### 2019-01-10 paper/tangotd.tex

>>>>

Normalization of $Z$. Since $Z=\sum \gamma^t P^t$, we have that
$(1-\gamma)Z$ is a stochastic matrix (thanks Yann). This might help with
normalization/detecting divergence. This translates as $\E_{s_2\sim \rho}
Z(s_1,s_2)=\frac{1}{1-\gamma}$ which is testable/enforceable. However, I
fear it might make the fixed point $Z(s_1,s_2)=\frac{1}{1-\gamma}$
attractive instead of repulsive, and it might also perturb initialization
(initializing $Z=\Id$ does not satisfy this normalization, so enforcing
it too early is basically like initializing to
$Z(s_1,s_2)=\frac{1}{1-\gamma}$ which empirically diverges).
